`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Get the "Bioninformatics" citation style definition form the zotero repository and initiate its usage;
Reformat author associations etc.;

---
title: "`flippant` -- An `R` package for the automated  analysis of dithionite 
  scramblase assays"
author: "Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Mike A. Goren ^‡^ and Anant K. Menon ^‡^"
date: "September 16, 2015"
output: 
#  word_document
  pdf_document:
    fig_caption: yes
#bibliography: flippant.bib
#csl: cell.csl
---

†

:    \
    Weill Cornell Medical College in Qatar, P.O.Box 24144, Doha, State of Qatar

‡

:   Department of Biochemistry, Weill Cornell Medical College, New York, NY 
    10065, USA

\*

:   To whom correspondence should be addresse: jog2030@qatar-med.cornell.edu

>>>>

---
title: "`flippant` -- An `R` package for the automated  analysis of dithionite 
  scramblase assays"
author: "Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Mike A. Goren ^‡^ and Anant K. Menon ^‡^"
date: "September 16, 2015"
output: 
#  word_document
  pdf_document:
    fig_caption: yes
#bibliography: flippant.bib
#csl: bioinformatics.csl
---

†
:    \
    Weill Cornell Medical College in Qatar, P.O.Box 24144, Doha, State of Qatar

‡
:   Department of Biochemistry, Weill Cornell Medical College, New York, NY 
    10065, USA

\*
:   To whom correspondence should be addressed: jog2030@qatar-med.cornell.edu
